---
title: "BLAS libraries benchmarks"
author: "Andrzej Wójtowicz"
output:
  html_document:
    keep_md: yes
---

Document generation date: `r Sys.time()`

This document presents timing results for BLAS ([Basic Linear Algebra Subprograms](https://en.wikipedia.org/wiki/Basic_Linear_Algebra_Subprograms)) libraries in [R](https://en.wikipedia.org/wiki/R_(programming_language)) on diverse CPUs and GPUs.

### Changelog

 * 2016-11-29: **results:** added Intel Xeon E3-1275 v5.
 * 2016-11-25: **results:** added Intel Atom C2758.
 * 2016-07-14: **results:** added Intel Core i5-6500; changed results view of gcbd benchmark to relative performance gain; changed reference CPU (Intel Pentium Dual-Core E5300) and GPU (NVIDIA GeForce GT 630M); **code:** fixed target architecture detection for Intel Core i5-6500-like CPUs in multi-threaded Atlas library; added info how to force target architecture in GotoBLAS2 and BLIS libraries.

```{r checkpoint, echo=FALSE, warning=FALSE, message=FALSE}
library(checkpoint)
checkpoint("2016-04-01", scanForPackages=FALSE, verbose=FALSE)

library(reshape2)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
```

## Table of Contents

 1. [Configuration](#configuration)
 2. [Results per host](#results-per-host)
    * [Intel Xeon E3-1275 v5](#intel-xeon-e3-1275-v5)
    * [Intel Core i7-4790K + MSI GeForce GTX 980 Ti Lightning](#intel-core-i7-4790k--msi-geforce-gtx-980-ti-lightning)
    * [Intel Core i5-4590 + NVIDIA GeForce GT 430](#intel-core-i5-4590--nvidia-geforce-gt-430)
    * [Intel Core i5-4590 + NVIDIA GeForce GTX 750 Ti](#intel-core-i5-4590--nvidia-geforce-gtx-750-ti)
    * [Intel Core i5-6500](#intel-core-i5-6500)
    * [Intel Core i5-3570](#intel-core-i5-3570)
    * [Intel Core i3-2120](#intel-core-i3-2120)
    * [Intel Core i3-3120M](#intel-core-i3-3120m)
    * [Intel Core i5-3317U + NVIDIA GeForce GT 630M](#intel-core-i5-3317u--nvidia-geforce-gt-630m)
    * [Intel Atom C2758](#intel-atom-c2758)
    * [Intel Pentium Dual-Core E5300](#intel-pentium-dual-core-e5300)
 3. [Results per library](#results-per-library)
    * [Netlib](#netlib)
    * [Atlas (st)](#atlas-st)
    * [OpenBLAS](#openblas)
    * [Atlas (mt)](#atlas-mt)
    * [GotoBLAS2](#gotoblas2)
    * [MKL](#mkl)
    * [BLIS](#blis)
    * [cuBLAS](#cublas)
 
***

## Configuration

**OS**: [Debian](https://www.debian.org/) Jessie, kernel 4.4

**R software**: [Microsoft R Open](https://mran.microsoft.com/open/) (3.2.4)

**Libraries**:

|CPU (single-threaded)|CPU (multi-threaded)|GPU|
|---|---|---|
|[Netlib](http://www.netlib.org/) (debian package, blas 1.2.20110419, lapack 3.5.0)|[OpenBLAS](http://www.openblas.net/) (debian package, 0.2.12)|[NVIDIA cuBLAS](https://developer.nvidia.com/cublas) (NVBLAS 6.5 + Intel MKL)|
|[ATLAS](http://math-atlas.sourceforge.net/) (debian package, 3.10.2)|[ATLAS](http://math-atlas.sourceforge.net/) (dev branch, 3.11.38)|   |
|   |[GotoBLAS2](https://prs.ism.ac.jp/~nakama/SurviveGotoBLAS2/) (Survive fork, 3.141)|   |
|   |[Intel MKL](https://mran.microsoft.com/download/) (part of RevoMath package, 3.2.4)|   |
|   |[BLIS](https://github.com/flame/blis) (dev branch, 0.2.0+/17.05.2016)|   |

**Hosts**:

|No.|CPU|GPU|
|---|---|---|
|1.|[Intel Xeon E3-1275 v5](http://ark.intel.com/products/88177/Intel-Xeon-Processor-E3-1275-v5-8M-Cache-3_60-GHz)| - |
|2.|[Intel Core i7-4790K](http://ark.intel.com/products/80807/Intel-Core-i7-4790K-Processor-8M-Cache-up-to-4_40-GHz) (OC 4.5 GHz)|[MSI GeForce GTX 980 Ti Lightning](https://us.msi.com/Graphics-card/GTX-980-Ti-LIGHTNING.html#hero-specification)|
|3.|[Intel Core i5-4590](http://ark.intel.com/products/80815/Intel-Core-i5-4590-Processor-6M-Cache-up-to-3_70-GHz)|[NVIDIA GeForce GT 430](http://www.geforce.com/hardware/desktop-gpus/geforce-gt-430/specifications)|
|4.|[Intel Core i5-4590](http://ark.intel.com/products/80815/Intel-Core-i5-4590-Processor-6M-Cache-up-to-3_70-GHz)|[NVIDIA GeForce GTX 750 Ti](http://www.geforce.com/hardware/desktop-gpus/geforce-gtx-750-ti/specifications)|
|5.|[Intel Core i5-6500](http://ark.intel.com/products/88184/Intel-Core-i5-6500-Processor-6M-Cache-up-to-3_60-GHz)| - |
|6.|[Intel Core i5-3570](http://ark.intel.com/products/65702/Intel-Core-i5-3570-Processor-6M-Cache-up-to-3_80-GHz)| - |
|7.|[Intel Core i3-2120](http://ark.intel.com/products/53426/Intel-Core-i3-2120-Processor-3M-Cache-3_30-GHz)| - |
|8.|[Intel Core i3-3120M](http://ark.intel.com/products/71465/Intel-Core-i3-3120M-Processor-3M-Cache-2_50-GHz)| - |
|9.|[Intel Core i5-3317U](http://ark.intel.com/products/65707/Intel-Core-i5-3317U-Processor-3M-Cache-up-to-2_60-GHz)|[NVIDIA GeForce GT 630M](http://www.geforce.com/hardware/notebook-gpus/geforce-gt-630m/specifications)|
|10.|[Intel Atom C2758](http://ark.intel.com/products/77988/Intel-Atom-Processor-C2758-4M-Cache-2_40-GHz)| - |
|11.|[Intel Pentium Dual-Core E5300](http://ark.intel.com/products/35300/Intel-Pentium-Processor-E5300-2M-Cache-2_60-GHz-800-MHz-FSB)| - |

**Benchmarks**: [R-benchmark-25](http://r.research.att.com/benchmarks/R-benchmark-25.R), [Revolution](https://gist.github.com/andrie/24c9672f1ea39af89c66#file-rro-mkl-benchmark-r), [Gcbd](https://cran.r-project.org/web/packages/gcbd/vignettes/gcbd.pdf).

```{r config, echo=FALSE}

HOSTNAMES = suppressWarnings(readLines("hosts-list.txt"))

BENCHMARKS = c("urbanek",
               "revolution",
               "gcbd")

LIBRARIES = c("netlib",
              "atlas_st",
              "openblas",
              "atlas_mt",
              "gotoblas2",
              "mkl",
              "blis",
              "cublas")

LIBRARY.REF  = "netlib"
HOST.REF     = "Intel Pentium Dual-Core E5300"
HOST.REF.SEC = "Intel Core i5-3317U"
HOST.REF.GPU = "NVIDIA GeForce GT 630M"

HOST.INFO.PATTERN = "host-info-<HOST>.log"
BENCHMARK.PATTERN = "test-<BENCHMARK>-<HOST>-<LIBRARY>.rds"

RESULTS.DIR = "results"
GEN.DIR     = "gen"
DATA.DIR    = file.path(GEN.DIR, "data")
IMAGES.DIR  = file.path(GEN.DIR, "img")

```

```{r read-write-data, echo=FALSE}

for (d in c(GEN.DIR, DATA.DIR, IMAGES.DIR))
    if (!dir.exists(d))
        dir.create(d)

hosts.info = data.frame(Host=character(), CPU=character(), GPU=character())

for (hostname in HOSTNAMES)
{
    fp = file.path(RESULTS.DIR, gsub("<HOST>", hostname, HOST.INFO.PATTERN))
    
    if (file.exists(fp))
    {
        dr = readLines(fp)
        dr = unname(sapply(dr, trimws))
        
        hosts.info = rbind(hosts.info,
            data.frame(Host= hostname, 
                       CPU = gsub("\\(.*?\\)", "", dr[1]), 
                       GPU = ifelse(length(dr)==3,
                        gsub("(NVIDIA|MSI).*\\[(.*)\\]", "\\1 \\2", dr[3]), NA)))
    } else {
        warning(paste("File", fp, "does not exist"))
    }
}

saveRDS(hosts.info, file.path(DATA.DIR, "hosts.info.rds"))


benchmark.results = data.frame(Host=character(), Benchmark=character(), 
                               Library=character(), Test=character(),
                               Runs=integer(), Size=integer(),
                               Time=numeric())

for (host in hosts.info$Host)
{
    for (benchmark in BENCHMARKS)
    {
        for (lib in LIBRARIES)
        {
            if (lib=="cublas" && is.na(hosts.info[which(hosts.info$Host==host),
                                                  "GPU"]))
                next
            
            fp = file.path(RESULTS.DIR, gsub("<HOST>", host, (
                                        gsub("<LIBRARY>", lib, ( 
                                        gsub("<BENCHMARK>", benchmark, BENCHMARK.PATTERN)))))
                           )
            
            if (file.exists(fp))
            {
                db = readRDS(fp)
                
                runs = NA
                if (length(attr(db, "runs"))==1) {
                    runs = attr(db, "runs")
                } else {
                    # gcbd
                    db = melt(cbind(db, runs=attr(db, "runs"), 
                                    size=attr(db, "size")), 
                              id.vars=c("runs", "size"), 
                              variable.name="name", 
                              value.name="time")
                    runs = db$runs
                }
                
                size = NA
                if ("size" %in% colnames(db)) # gcbd
                    size = db$size
                
                benchmark.results = rbind(benchmark.results,
                    data.frame(Host=host, Benchmark=benchmark, 
                               Library=lib, Test=db$name, 
                               Runs=runs, Size=size,
                               Time=db$time))
            } else {
                warning(paste("File", fp, "does not exist"))
            }
        }
    }
}

saveRDS(benchmark.results, file.path(DATA.DIR, "benchmark.results.rds"))

```

```{r per-host, echo=FALSE, results='asis'}

cat("# Results per host\n\n")

for (host in hosts.info$Host)
{
    host.cpu = hosts.info[which(hosts.info$Host==host), "CPU"]
    host.gpu = hosts.info[which(hosts.info$Host==host), "GPU"]
    
    cat(paste("##", host.cpu))
    
    if (!is.na(host.gpu))
        cat(paste(" +", host.gpu))
    
    cat("\n\n\n\n")
    
    for (benchmark in BENCHMARKS)
    {
        cat(paste0("### ", 
                    ifelse(benchmark=="urbanek", "R-benchmark-25", # fix to common name
                           paste(toupper(substring(benchmark, 1,1)), 
                                 substring(benchmark, 2), " benchmark", sep="", collapse=" ")), 
                   "\n\n"))
        
        testnames = benchmark.results %>% 
            filter(Benchmark == benchmark) %>% 
            select(Test) %>% 
            unique
        
        if (benchmark == "urbanek")
            # remove tests with almost the same results
            testnames = testnames %>% filter(row_number() %in% c(4, 5, 7, 8, 9, 10, 15))
        
        
        for (i in 1:nrow(testnames)) 
        {
            test = as.character(testnames[i, "Test"])

            data.to.plot = benchmark.results %>% 
                filter(Host == host & Benchmark == benchmark &
                       Test == test)
            
            data.to.plot = data.to.plot %>% 
                    mutate(Time=replace(Time, Time==0, 5e-05), 
                           PerfGain=data.to.plot[which(data.to.plot$Library==LIBRARY.REF), "Time"]/Time)
            
            renamedLibs = list(
                "cuBLAS"="cublas",
                "BLIS"="blis",
                "MKL"="mkl",
                "ATLAS (mt)"="atlas_mt",
                "OpenBLAS"="openblas",
                "GotoBLAS2"="gotoblas2",
                "ATLAS (st)"="atlas_st",
                "Netlib"="netlib")
            
            if (benchmark != "gcbd")
                levels(data.to.plot$Library) = renamedLibs
            else
                levels(data.to.plot$Library) = rev(renamedLibs)
            
            
            data.to.plot = data.to.plot %>% 
                mutate(Color=sapply(Library, function(x){
                    if(x=="Netlib") "A" 
                    else if(x=="ATLAS (st)") "B" 
                    else if(x=="cuBLAS") "D" 
                    else "C"}))
            
            cat(paste0("#### ", # fix urbanek errors in names
                       gsub(" \\(.*\\)", "", 
                            gsub("Linear regr. over a 3000x3000 matrix", 
                                 "Linear regr. over a 2000x2000 matrix", 
                                 gsub("Eigenvalues of a 640x640", 
                                      "Eigenvalues of a 600x600", test))
                            )
                ), 
            "\n\n")
            
            if (any(data.to.plot$Time == Inf, na.rm = TRUE))
            {
                cat(paste(as.character(data.to.plot[which(data.to.plot$Time == Inf), "Library"])), "hangs in this test\n\n")
            }
            
            if (any(is.na(data.to.plot$Time)))
            {
                cat(paste(unique(as.character(data.to.plot[which(is.na(data.to.plot$Time)), "Library"]))), "crashes in this test\n\n")
            }
            
            data.to.plot = data.to.plot[data.to.plot$Time != Inf & !is.na(data.to.plot$Time), ]
            
            image.path = file.path(IMAGES.DIR,
               paste0("img_ph", 
                      "_h", which(host == hosts.info$Host),
                      "_b", which(benchmark == BENCHMARKS),
                      "_t", i,
                      ".png"))
            
            if (benchmark != "gcbd")
                cat(paste0("Time in seconds - ", data.to.plot$Runs[1], " runs - lower is better\n\n"))
            else
                cat(paste0("Performance gain regarding matrix size - reference: ", names(which(renamedLibs==LIBRARY.REF)), " - from ", max(data.to.plot$Runs), " to ", min(data.to.plot$Runs), " runs - higher is better\n\n"))
            
            myColors = c("#E6191A", "#F25F1E", "#636363", "#5AAC45")
            names(myColors) = levels(data.to.plot$Color)
            colScale = scale_fill_manual(name = "Color", values = myColors)
            
            if (benchmark != "gcbd")
            {
            png(image.path, width=600, height=35*nrow(data.to.plot))
                print(ggplot(data.to.plot, aes(x=reorder(Library, -Time), y=Time, fill=Color)) +
                    theme_classic() + 
                    theme(
                        panel.border = element_blank(),
                        axis.title.x=element_blank(),
                        axis.title.y=element_blank(),
                        axis.text.x = element_text(colour="grey60"),
                        axis.ticks.x=element_line(color="grey60"),
                        axis.ticks.y=element_line(color="grey60"),
                        legend.position="none"
                    ) +
                    scale_y_continuous(expand = c(0, 0), 
                                       limits = c(0, 1.20*max(data.to.plot$Time))) +
                    geom_bar(stat="identity", width=.7) + 
                    coord_flip() + 
                    geom_text(aes(y=Time, x=Library, label=format(Time, digits=2, nsmall=2)), hjust=-0.25, size=3, colour="grey45") +
                    geom_text(aes(y=1.2*max(data.to.plot$Time), x=Library, label=paste0("x", trimws(format(PerfGain, digits=1, nsmall=1)))), hjust=1, size=4) +
                    geom_hline(yintercept = 0, color="grey") + 
                    geom_vline(xintercept = 0.4, color="grey") +
                    annotate("text", x=nrow(data.to.plot)+0.55, y=1.2*max(data.to.plot$Time), label="Performance gain", hjust=1) +
                    colScale
                ) 
            dev.off()
            
            cat(paste0("![](", image.path, ")\n\n\n\n"))
            
            } else {
            rbColors = c("#F40000","#FF8000","#0094FF","#E900FF","#B35807","#7F00FF","#FFBC70","#00DD0E")
                
            png(image.path, width=600, height=400, type="cairo")
                print(ggplot(data.to.plot, 
                             aes(x=Size, y=PerfGain, group=Library, color=Library,
                                 shape=Library, fill=Library)) +
                    theme_classic() +
                        theme(
                            panel.border = element_blank(),
                            axis.title.x=element_blank(),
                            axis.title.y=element_blank(),
                            axis.text.x = element_text(colour="grey60"),
                            axis.text.y = element_text(colour="grey60"),
                            axis.ticks.x=element_line(color="grey60"),
                            axis.ticks.y=element_line(color="grey60"),
                            legend.margin=unit(c(-13,8), "mm"),
                            legend.title=element_blank()
                        ) +
                    geom_line(size=1) + 
                    geom_point(size=2, color="grey30") +
                    scale_x_log10(expand=c(0,0), 
                                  breaks=c(100, 200, 400, 800, 1600, 3200, 5000),
                                  limits=c(90, 5500)) +
                    scale_y_continuous(expand = c(0, 0)) +
                    geom_hline(yintercept = 0, color="grey") + 
                    geom_vline(xintercept = 90, color="grey") +
                    scale_shape_manual(values=c(21,24,22,25,23,21,22,23)) +
                    scale_color_manual(values=rbColors) +
                    scale_fill_manual(values=rbColors)
                    
                )
            dev.off()
            
            cat(paste0("![](", image.path, ")\n\n\n\n"))
            
            }
            
            
        }
        
        
    }
}

```




```{r per-library, echo=FALSE, results='asis'}

cat("# Results per library\n\n")

renamedLibs = list(
    "cublas"="cuBLAS",
    "blis"="BLIS",
    "mkl"="MKL",
    "atlas_mt"="ATLAS (mt)",
    "openblas"="OpenBLAS",
    "gotoblas2"="GotoBLAS2",
    "atlas_st"="ATLAS (st)",
    "netlib"="Netlib")

for (lib in LIBRARIES)
{
    cat(paste("##", renamedLibs[[lib]]))
    
    cat("\n\n\n\n")
    
    for (benchmark in BENCHMARKS)
    {
        cat(paste0("### ", 
                    ifelse(benchmark=="urbanek", "R-benchmark-25", # fix to common name
                           paste(toupper(substring(benchmark, 1,1)), 
                                 substring(benchmark, 2), " benchmark", sep="", collapse=" ")), 
                   "\n\n"))
        
        testnames = benchmark.results %>% 
            filter(Benchmark == benchmark) %>% 
            select(Test) %>% 
            unique
        
        if (benchmark == "urbanek")
            # remove tests with almost the same results
            testnames = testnames %>% filter(row_number() %in% c(4, 5, 7, 8, 9, 10, 15))
        
        
        for (i in 1:nrow(testnames)) 
        {
            test = as.character(testnames[i, "Test"])

            data.to.plot = benchmark.results %>% 
                filter(Library == lib & Benchmark == benchmark &
                       Test == test)
            
            data.to.plot = data.to.plot %>% rowwise() %>%
                mutate(CPUGPU=hosts.info[which(hosts.info$Host==Host), ifelse(lib!="cublas", "CPU", "GPU")])
            
            if (benchmark != "gcbd")
            {
                if (lib!="cublas")
                {
                    if (data.to.plot[which(hosts.info$CPU==HOST.REF), "Time"]!=Inf) {
                        data.to.plot = data.to.plot %>%
                          mutate(Time=replace(Time, Time==0, 5e-05),
                                 PerfGain=data.to.plot[which(hosts.info$CPU==HOST.REF), "Time"]/Time)
                    } else {
                        data.to.plot = data.to.plot %>%
                          mutate(Time=replace(Time, Time==0, 5e-05),
                                 PerfGain=data.to.plot[which(hosts.info$CPU==HOST.REF.SEC), "Time"]/Time)
                    }
                } else {
                    data.to.plot = data.to.plot %>%
                      mutate(Time=replace(Time, Time==0, 5e-05),
                             PerfGain=data.to.plot[which(filter(hosts.info, !is.na(GPU))$GPU==HOST.REF.GPU), ][["Time"]]/Time)
                }
            } else {
                if (lib!="cublas") 
                {
                    data.to.plot = data.to.plot %>%
                      mutate(Time=replace(Time, Time==0, 5e-05))
                    
                    data.to.plot$PerfGain = 
                        data.to.plot[which(data.to.plot$CPUGPU==HOST.REF), ][["Time"]]/data.to.plot$Time
                } else {
                    data.to.plot = data.to.plot %>%
                      mutate(Time=replace(Time, Time==0, 5e-05))
                    data.to.plot$PerfGain = 
                        data.to.plot[which(data.to.plot$CPUGPU==HOST.REF.GPU), ][["Time"]]/data.to.plot$Time
                }
            }
            
            
            
            cat(paste0("#### ", # fix urbanek errors in names
                       gsub(" \\(.*\\)", "", 
                            gsub("Linear regr. over a 3000x3000 matrix", 
                                 "Linear regr. over a 2000x2000 matrix", 
                                 gsub("Eigenvalues of a 640x640", 
                                      "Eigenvalues of a 600x600", test))
                            )
                ), 
            "\n\n")
            
            if (any(is.na(data.to.plot$Time)))
            {
                cat(paste("Library crashes on", unique(as.character(as.data.frame(data.to.plot)[which(is.na(data.to.plot$Time)), "CPUGPU"]))), "in this test\n\n")
            }
            
            if (any(data.to.plot$Time == Inf, na.rm = TRUE))
            {
                cat(paste("Library hangs on", as.character(as.data.frame(data.to.plot)[which(data.to.plot$Time == Inf), "CPUGPU"])), "in this test\n\n")
            }
            
            data.to.plot = data.to.plot[data.to.plot$Time != Inf & !is.na(data.to.plot$Time), ]
            
            image.path = file.path(IMAGES.DIR,
               paste0("img_pl", 
                      "_l", which(lib == LIBRARIES),
                      "_b", which(benchmark == BENCHMARKS),
                      "_t", i,
                      ".png"))
            
            if (benchmark != "gcbd")
                cat(paste0("Time in seconds - ", data.to.plot$Runs[1], " runs - lower is better\n\n"))
            else
                cat(paste0("Performance gain regarding matrix size - reference: ", ifelse(lib!="cublas", HOST.REF, HOST.REF.GPU), " - from ", max(data.to.plot$Runs), " to ", min(data.to.plot$Runs), " runs - higher is better\n\n"))
            
            
            myColors = c("#636363", "#5AAC45", "#636363", "#636363", "#636363", "#636363", "#636363", "#636363", "#636363", "#E6191A")
            if (lib=="cublas")
                myColors = c("#5AAC45", "#636363", "#636363", "#E6191A")
            
            colScale = scale_fill_manual(name = "Color", values = myColors)
            
            data.to.plot = unique(select(data.to.plot, -Host))
            
            if (benchmark != "gcbd")
            {
            png(image.path, width=600, height=50*length(unique(data.to.plot$CPUGPU))+ifelse(nrow(data.to.plot)>1, 0, 20))
                print(ggplot(data.to.plot, aes(x=reorder(CPUGPU, -Time), y=Time,
                                               fill=CPUGPU)) +
                    theme_classic() + 
                    theme(
                        panel.border = element_blank(),
                        axis.title.x=element_blank(),
                        axis.title.y=element_blank(),
                        axis.text.x = element_text(colour="grey60"),
                        axis.ticks.x=element_line(color="grey60"),
                        axis.ticks.y=element_line(color="grey60"),
                        legend.position="none"
                    ) +
                    scale_y_continuous(expand = c(0, 0), 
                                       limits = c(0, 1.20*max(data.to.plot$Time))) +
                    geom_bar(stat="identity", width=.7) + 
                    coord_flip() + 
                    geom_text(aes(y=Time, x=CPUGPU, label=format(Time, digits=2, nsmall=2)), hjust=-0.25, size=3, colour="grey45") +
                    geom_text(aes(y=1.2*max(data.to.plot$Time), x=CPUGPU, label=paste0("x", trimws(format(PerfGain, digits=1, nsmall=1)))), hjust=1, size=4) +
                    geom_hline(yintercept = 0, color="grey") + 
                    geom_vline(xintercept = 0.4, color="grey") +
                    annotate("text", x=length(unique(data.to.plot$CPUGPU))+ifelse(nrow(data.to.plot)>1, 0.55, 0.45), y=1.2*max(data.to.plot$Time), label="Performance gain", hjust=1) +
                    colScale
                ) 
            dev.off()
            
            cat(paste0("![](", image.path, ")\n\n\n\n"))
            
            } else {
                
            rbColors = c("#F40000","#FF8000","#0094FF","#7F00FF","#E900FF","#00DD0E","#B35807", "#7F006E", "#F4DD00", "#000000")
            
            png(image.path, width=700, height=400, type="cairo")
                print(ggplot(data.to.plot, 
                             aes(x=Size, y=PerfGain, group=CPUGPU, color=CPUGPU,
                                 shape=CPUGPU, fill=CPUGPU)) +
                    theme_classic() +
                        theme(
                            panel.border = element_blank(),
                            axis.title.x=element_blank(),
                            axis.title.y=element_blank(),
                            axis.text.x = element_text(colour="grey60"),
                            axis.text.y = element_text(colour="grey60"),
                            axis.ticks.x=element_line(color="grey60"),
                            axis.ticks.y=element_line(color="grey60"),
                            legend.title=element_blank()
                        ) +
                    geom_line(size=1) + 
                    geom_point(size=2, color="grey30") +
                    scale_x_log10(expand=c(0,0), 
                                  breaks=c(100, 200, 400, 800, 1600, 3200, 5000),
                                  limits=c(90, 5500)) +
                    scale_y_continuous(expand = c(0, 0)) +
                    geom_hline(yintercept = 0, color="grey") + 
                    geom_vline(xintercept = 90, color="grey") +
                    scale_shape_manual(values=c(25,24,22,21,23,25,24,22,21,23)) +
                    scale_color_manual(values=rbColors) +
                    scale_fill_manual(values=rbColors)
                    
                )
            dev.off()
            
            cat(paste0("![](", image.path, ")\n\n\n\n"))
            
            }
            
            
        }
        
        
    }
}

```

